initial_analysis_notebook

### 2021-04-27 exploratory/notebook/initial_analysis/initial_analysis_notebook.Rmd
remove hist v toxin

## Does toxin explain histological findings?

```{r}
toxin %>% 
  mutate(mouse_id = ifelse(toxin_sample_type == 'cecalcon', 
                           gsub('C$', '', mouse_id), mouse_id)) %>% 
  group_by(mouse_id) %>% 
  mutate(last_sample = max(toxin_sample_day)) %>% 
  filter(toxin_sample_day == last_sample) %>% 
  left_join(select(histology, mouse_id, summary_score), by = c('mouse_id')) %>% 
  left_join(mouse_by_outcome, by = c('mouse_id')) %>% 
  filter(!is.na(summary_score)) %>% 
  ggplot(aes(y = Log_repiricoal_dilution, x = summary_score)) + 
    geom_dotplot(binaxis = 'y', stackdir = 'center', dotsize = 0.5,
                 aes(fill = as.factor(summary_score))) + 
    #stat_summary(fun.data = 'median_hilow', fun.args = (conf.int=0.5),
    #             aes(color = as.factor(summary_score))) +
    #geom_jitter(width = 0.25, alpha = 0.5) + 
    scale_color_manual(values = donor_colors) + 
    scale_fill_manual(values = donor_colors) + 
    theme_bw() + 
    scale_x_continuous(breaks = 0:10) + 
    guides(color = 'none', fill = 'none')

toxin %>% 
  mutate(mouse_id = ifelse(toxin_sample_type == 'cecalcon', 
                           gsub('C$', '', mouse_id), mouse_id)) %>% 
  group_by(mouse_id) %>% 
  mutate(last_sample = max(toxin_sample_day)) %>% 
  filter(toxin_sample_day == last_sample) %>% 
  left_join(select(histology, mouse_id, epithelial_damage), by = c('mouse_id')) %>% 
  left_join(mouse_by_outcome, by = c('mouse_id')) %>% 
  filter(!is.na(epithelial_damage)) %>% 
  ggplot(aes(y = Log_repiricoal_dilution, x = epithelial_damage, 
             color = as.factor(epithelial_damage))) + 
    geom_dotplot(binaxis = 'y', stackdir = 'center', dotsize = 0.5,
                 aes(fill = as.factor(epithelial_damage))) + 
    #stat_summary(fun.data = 'median_hilow', fun.args = (conf.int=0.5)) +
    #geom_jitter(width = 0.25, alpha = 0.5) + 
    scale_color_manual(values = donor_colors) + 
    scale_fill_manual(values = donor_colors) + 
    theme_bw() + 
    scale_x_continuous(breaks = 0:10) + 
    guides(color = 'none', fill = 'none')

# is this relevant?
```

>>>>

```{r}
## Does toxin explain histological findings?
#toxin %>% 
#  mutate(mouse_id = ifelse(toxin_sample_type == 'cecalcon', 
#                           gsub('C$', '', mouse_id), mouse_id)) %>% 
#  group_by(mouse_id) %>% 
#  mutate(last_sample = max(toxin_sample_day)) %>% 
#  filter(toxin_sample_day == last_sample) %>% 
#  left_join(select(histology, mouse_id, summary_score), by = c('mouse_id')) %>% 
#  left_join(mouse_by_outcome, by = c('mouse_id')) %>% 
#  filter(!is.na(summary_score)) %>% 
#  ggplot(aes(y = Log_repiricoal_dilution, x = summary_score)) + 
#    geom_dotplot(binaxis = 'y', stackdir = 'center', dotsize = 0.5,
#                 aes(fill = as.factor(summary_score))) + 
#    #stat_summary(fun.data = 'median_hilow', fun.args = (conf.int=0.5),
#    #             aes(color = as.factor(summary_score))) +
#    #geom_jitter(width = 0.25, alpha = 0.5) + 
#    scale_color_manual(values = donor_colors) + 
#    scale_fill_manual(values = donor_colors) + 
#    theme_bw() + 
#    scale_x_continuous(breaks = 0:10) + 
#    guides(color = 'none', fill = 'none')
#
#toxin %>% 
#  mutate(mouse_id = ifelse(toxin_sample_type == 'cecalcon', 
#                           gsub('C$', '', mouse_id), mouse_id)) %>% 
#  group_by(mouse_id) %>% 
#  mutate(last_sample = max(toxin_sample_day)) %>% 
#  filter(toxin_sample_day == last_sample) %>% 
#  left_join(select(histology, mouse_id, epithelial_damage), by = c('mouse_id')) %>% 
#  left_join(mouse_by_outcome, by = c('mouse_id')) %>% 
#  filter(!is.na(epithelial_damage)) %>% 
#  ggplot(aes(y = Log_repiricoal_dilution, x = epithelial_damage, 
#             color = as.factor(epithelial_damage))) + 
#    geom_dotplot(binaxis = 'y', stackdir = 'center', dotsize = 0.5,
#                 aes(fill = as.factor(epithelial_damage))) + 
#    #stat_summary(fun.data = 'median_hilow', fun.args = (conf.int=0.5)) +
#    #geom_jitter(width = 0.25, alpha = 0.5) + 
#    scale_color_manual(values = donor_colors) + 
#    scale_fill_manual(values = donor_colors) + 
#    theme_bw() + 
#    scale_x_continuous(breaks = 0:10) + 
#    guides(color = 'none', fill = 'none')
#
# not applicable to our story
```
